Final Paper

### 2016-08-09 paper/paper.Rmd
paper updated'

Our first hypothesis was that successful businesses would be clustered at certain points. We first tried to plot this information with points on a map using longitude and latitude of the businesses.  Points with different sizes stacked up on each other, so the size and color of the points did not tell much information. Even though 900+ points were plotted, there were really only six primary clusters of points so there was no point in having so many small individual points.

Instead, we ended up with a bar graph, which clearly shows which state has the most number of businesses with over 300 reviews. There were 6 distinct regions in total. Interestingly, the graph shows that the majority of the businesses is located in two states: about 62% of the filtered businesses were located in Nevada and another 31% was in Arizona. 
```{r business, echo = FALSE, fig.align = "center",message = FALSE, fig.height = 3.5}
ggplot(ratings_business,aes(x=stars, y=count)) +  
  geom_point(col = rgb(0,0,1,0.25), pch = 16, cex = 2) +
  scale_y_continuous(limits=c(300,5000)) +
  xlab("Star Ratings") + 
  ylab("Review Counts") +
  theme(text = element_text(family = "Times New Roman"))

@@

As such, six major attributes were chosen. There were slight differences in star ratings based on some categories. For example, businesses that accept credit cards seemed to have higher ratings compared to those that don't. Interestingly, restaurants that do not offer delivery showed slightly higher star ratings than those who do. There were no major findings from the plots, however. Except for slight differences in average ratings of certain attributes, there was no significant difference evident. The user review ratings were evenly spread out even if the specific attribute existed or not. Our findings pointed out that business attributes do not have huge influences over user ratings.
```{r attributes, echo = FALSE, fig.align = "center"}
business_attributes <- business %>% 
  filter(count > 300) %>% 
  select(-open, -count, -categories, -noise, -attire) %>% 
  gather(key = Attribute, value = Val, -business_id, -state, -stars) %>% 
  na.omit

@@

```{r density, echo = FALSE, fig.align = "center"}
selected_users <- users %>% 
  filter(review_count > 50) %>% 
  select(name, user_id, review_count)

@@

@@

@@

>>>>

Our first hypothesis was that successful businesses would be clustered at certain states. We examined the data set and wanted to know about the relationship between the number of reviews and the star ratings. It turned out that when number of reviews increases, the star ratings gets clustered around 3.5 out of 5. Hence, we hypothesized that high number of reviews, especially those locations with most reviewed businesses, will have positive influence to the star ratings.

We first tried to plot this information with points on a map using longitude and latitude of the businesses. Points with different sizes stacked up on each other, so the size and color of the points did not tell much information. Even though 900+ points were plotted, there were really only six primary clusters of points so there was no point in having so many small individual points.

Instead, we ended up with a bar graph, which clearly shows which state has the most number of businesses with over 300 reviews. There were 6 distinct regions in total. Interestingly, the graph shows that the majority of the businesses is located in two states: about 62% of the filtered businesses were located in Nevada and another 31% was in Arizona. 
```{r business, echo = FALSE, fig.align = "center", message = FALSE, fig.height = 3.5, warning = FALSE}
ggplot(ratings_business,aes(x=stars, y=count)) +  
  geom_point(col = rgb(0,0,1,0.25), pch = 16, cex = 2) +
  scale_y_continuous(limits=c(300,5000)) +
  xlab("Star Ratings") + 
  ylab("Review Counts") +
  theme(text = element_text(family = "Times New Roman"))

@@

As such, six major attributes were chosen. There were slight differences in star ratings based on some categories. For example, businesses that accept credit cards seemed to have higher ratings compared to those that don't. Interestingly, restaurants that do not offer delivery showed slightly higher star ratings than those who do. There were no major findings from the plots, however. Except for slight differences in average ratings of certain attributes, there was no significant difference evident. The user review ratings were evenly spread out even if the specific attribute existed or not. Our findings pointed out that business attributes do not have huge influences over user ratings.
```{r attributes, echo = FALSE, fig.align = "center", message = FALSE}
business_attributes <- business %>% 
  filter(count > 300) %>% 
  select(-open, -count, -categories, -noise, -attire) %>% 
  gather(key = Attribute, value = Val, -business_id, -state, -stars) %>% 
  na.omit

@@

```{r density, echo = FALSE, fig.align = "center", message = FALSE}
selected_users <- users %>% 
  filter(review_count > 50) %>% 
  select(name, user_id, review_count)

@@

There is a close relationship between star ratings and number of reviews--the popularity of the business. There are certain locations where most reviewed businesses are clustered; hence, location also has some influence over the star ratings. However, no significant correlations between business attributes and the review ratings were found.

@@

Lastly, by examining the behavior of users while travelling showed that most users tend to give mediocre ratings when in unfamiliar places. On the other hand, the ratings were evenly distributed while in familiar locations. Surprisingly the mean of each situation was about the same.

@@

At last, we could use full data set instead of an academic, truncated data provided for data challenge. This way we could utilize more information to make even accurate plots and analysis. Using this, a comparison of user trends in different countries will be interesting for further investigation.
